A Java Framework For Embarrassingly Parallel Problems

### 2013-12-11 paper/paper.tex
more paper stuff

\doublespacing
\begin{document}
\title{A Java Framework For Embarrassingly Parallel Problems}
\author{Jacob Schwartz}
\maketitle

@@

\begin{figure}
    \begin{center}
        \resizebox{5.2in}{!}{\includegraphics{experiment/time.png}}
    \end{center}
    \caption{Runtimes for the Ka/Ks Calculator though the framework}
    \label{fig:kaksgraph}
\end{figure}

Figure \ref{fig:kaksgraph} summarized the results; each line shows the time
taken for each chunk of the data. As the numbers of threads increases, the
runtime of the program decreases exponentially. In a few cases, there was an
increase in time when attempting to max out the CPU usage. This occurs because
the framework has to wait for the CPU to be finished with its previous work
before it can start any further jobs.

TODO(Keep?): In the cases when the framework executed faster while the CPU was 
maxed out, it was only faster a minute at the most. However, running the 
framework at 50\% of the CPU is more efficient than running using 100\% of the 
CPU. The runtime drop achieved when using 100\% of the CPU versus 50\% is not 
large enough to warrant using all of the machine's power.

\subsection{Octupus}

@@

\begin{table}
    \begin{center}
    \begin{tabular}{|l|l|l|}
    \hline
        Number of Sequences & Minimum Similarity & Time(s) \\ \hline
        1500                & 90\%               & 99      \\
        ~                   & 95\%               & 115     \\
        ~                   & 97\%               & 131     \\ \hline
        6500                & 90\%               & 425     \\
        ~                   & 95\%               & 496     \\
        ~                   & 97\%               & 603     \\ \hline
    \end{tabular}
    \caption{Times from serial octupus at various similarity levels.}
    \end{center}
    \label{tab:octu1}
\end{table}

\begin{table}
    \begin{center}
    \begin{tabular}{|l|l|l|}
        \hline
        Number of Sequences & Number of Workers & Time(s) \\ \hline
        1500                & 6                 & 34      \\
        ~                   & 8                 & 27      \\
        ~                   & 10                & 27      \\ \hline
        6500                & 6                 & 127     \\
        ~                   & 8                 & 127     \\
        ~                   & 10                & 123     \\ \hline
    \end{tabular}
    \caption{Times from octupus through the framework at 97\% similarirty.}
    \end{center}
    \label{tab:octu2}
\end{table}

@@

It is clear that the framework provides an effective yet simple to use module to
add parallelism to a specific class of file-oriented embarrassingly parallel
problems. Two sentences with specifics from the graphs. More self-praise

@@

\begin{thebibliography}{1}
\bibitem{kaks}
Zhang Z, Li J, Zhao XQ, Wang J, Wong GK, Yu J., \emph{Ka/Ks Calculator: 
calculating Ka and Ks through model selection and model averaging},
Genomics Proteomics Bioinformatics, November 2006.
\bibitem{cloud}
Crap, crap and Crap
\end{thebibliography}

>>>>

% \doublespacing
\begin{document}
\title{A Java Framework For Embarrassingly Parallel Problems}
\author{Jacob Schwartz}
\maketitle

@@

\begin{figure}
    \begin{center}
        \resizebox{4.7in}{!}{\includegraphics{experiment/time.png}}
    \end{center}
    \caption{Runtimes for the Ka/Ks Calculator though the framework}
    \label{fig:time}
\end{figure}

\begin{figure}
    \begin{center}
        \resizebox{4.7in}{!}{\includegraphics{experiment/speedup.png}}
    \end{center}
    \caption{Speedup of Ka/Ks Calculator program}
    \label{fig:speedup}
\end{figure}

Figure \ref{fig:time} summarized the results; each line shows the time taken for
each chunk of the data. As the numbers of threads increases, the runtime of the
program decreases exponentially. In a few cases, there was an increase in time
when attempting to max out the CPU usage. This occurs because the framework has
to wait for the CPU to be finished with its previous work before it can start
any further jobs.

Figure \ref{fig:speedup} shows the speedup of the Ka/Ks Calculator program. 
In most of the samples, the speedup seems to level off between 6 to 10 workers,
and even goes down when increased to 16 workers. Running the framework at 50\% 
of the CPU is more efficient than running using 100\% of the CPU in this 
situation. The decrease in speedup from 8 workers to 16 workers shows that TODO.
This is not true of all case, as seen in sample E. This sample has a higher
speedup at 16 workers because the piece of work that comes Xth in the sample
takes the longest. With 16 workers, this chunk is started immediately instead of
most of the way through the total runtime of the framework.
\subsection{Octupus}

@@

\begin{table}
    \begin{center}
    \begin{tabular}{|l|l|l|}
    \hline
        Number of Sequences & Minimum Similarity & Time(s) \\ \hline
        1500                & 90\%               & 99      \\
        ~                   & 95\%               & 115     \\
        ~                   & 97\%               & 131     \\ \hline
        6500                & 90\%               & 425     \\
        ~                   & 95\%               & 496     \\
        ~                   & 97\%               & 603     \\ \hline
    \end{tabular}
    \caption{Times from serial octupus at various similarity levels}
    \end{center}
    \label{tab:octu1}
\end{table}

\begin{table}
    \begin{center}
    \begin{tabular}{|l|l|l|}
        \hline
        Number of Sequences & Number of Workers & Time(s) \\ \hline
        1500                & 6                 & 34      \\
        ~                   & 8                 & 27      \\
        ~                   & 10                & 27      \\ \hline
        6500                & 6                 & 127     \\
        ~                   & 8                 & 127     \\
        ~                   & 10                & 123     \\ \hline
    \end{tabular}
    \caption{Times from octupus through the framework at 97\% similarirty}
    \end{center}
    \label{tab:octu2}
\end{table}

@@

It is clear that the framework provides an effective yet simple to use module to
add parallelism to a specific class of file-oriented embarrassingly parallel
problems. Two sentences with specifics from the graphs. More self-praise TODO

@@

\begin{thebibliography}{1}
\bibitem{kaks}
Zhang Z, Li J, Zhao XQ, Wang J, Wong GK, Yu J., \emph{Ka/Ks Calculator: 
calculating Ka and Ks through model selection and model averaging},
Genomics Proteomics Bioinformatics, November 2006.
\bibitem{cloud}
Gunarathne, T., Wu, T.-L., Choi, J. Y., Bae, S.-H. and Qiu, J., \emph{Cloud
computing paradigms for pleasingly parallel biomedical applications},
Concurrency and Computation: Practice and Experience, December 2011.
\end{thebibliography}
